\LARGE \bf Approximately Orchestrated Road Traffic Automata\\ a General Traffic Simulation Framework

### 2012-03-14 papers/itsc_2012/final.tex
a few mistakes fixed

Likewise, intersections check for collisions by examining the turn each agent is
performing and verifying that no other agent is simultaneously performing a
conflicting turn. AORTA has a low-granularity model of turn conflict. If two
vehicles at any point along two different turns could ever come into contact,
then the turns are always in conflict, no matter where the agents actually are
along that turn. This is visualized in figure \ref{fig:conflicts}. The
alternative of tiling intersections \cite{JAIR08-dresner} would provide more
granularity, but it adds computational complexity and would be impractical for
many of the complex intersection geometries inferred from OSM.

@@

A behavior's interaction with an intersection policy amounts to polling it with
the turn the agent wants to perform, the distance away the agent currently is,
and how long the agent has been waiting (so policies can enforce a required
delay before entering the intersection). The intersection policy simply orders
the agent to ``stop'' or ``proceed.'' The acceleration chosen to avoid entering
an intersection attempts to account for crosswalks by ending a configurable
threshold before the end of a traversable.

@@

\section{Agent Behaviors}

@@

A behavior's interaction with an intersection policy amounts to polling it with
the turn the agent wants to perform, the distance away the agent currently is,
and how long the agent has been waiting (so policies can enforce a required
delay before entering the intersection). The intersection policy simply orders
the agent to ``stop'' or ``proceed.'' The acceleration chosen to avoid entering
an intersection attempts to account for crosswalks by ending a configurable
threshold before the end of a traversable.

>>>>

Intersections check for collisions by examining the turn each agent is
performing and verifying that no other agent is simultaneously performing a
conflicting turn. AORTA has a low-granularity model of turn conflict. If two
vehicles at any point along two different turns could ever come into contact,
then the turns are always in conflict, no matter where the agents actually are
along that turn. This is visualized in figure \ref{fig:conflicts}. The
alternative of tiling intersections \cite{JAIR08-dresner} would provide more
granularity, but it adds computational complexity and would be impractical for
many of the complex intersection geometries inferred from OSM.

@@

A behavior's interaction with an intersection policy amounts to polling it with
the turn the agent wants to perform, the distance away the agent currently is,
and how long the agent has been waiting (so policies can enforce a required
delay before entering the intersection). The intersection policy simply orders
the agent to ``stop'' or ``proceed.'' \commentd{I'm not sure this fits in the
default behavior later anymore; just delete it?} The acceleration chosen to
avoid entering an intersection attempts to account for crosswalks by ending a
configurable threshold before the end of a traversable.

@@

\subsection{Agent Behaviors}

@@
